---
title: "Code Walkthrough"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(maps)
library(ncdf4)
library(zoo)
library(plot3D)
library(ggplot2)
# Set the working directory to source file location:
```


## Data Processing
In order to get the global & country avergaes significant processing happened of the data. This was time & resource intensive. To run the data youself with more recent data you can execute the following code chunk; otherwise skip this step. The aggregated data that it produces is included in the repository.

```{r processing, eval=FALSE}
source('initial_proccessing.R')
# Creates the country grid; commented out because file is static & included:
# create_country_grid_mapping()

# Aggregate average country & world NO2:
countries <- c("Brazil", "Canada", "China", "Germany", "India", "Iran", "Italy", "Japan", "Russia", "Saudi Arabia", "USA")
calculate_daily_average_no2(countries)
```

Instead of running this every time it's easist to just open the csv files by sourcing `open_data.R`. This should populate your environment with all the data & variables used further.
```{r open_data}
source('open_data.R')
```

## Opening Individual Data files
```{r}
filename = "Sample_no2_data_07182020.he5"
ncin <- nc_open(filename)
no2 <- t(ncvar_get(ncin,"Data Fields/ColumnAmountNO2CloudScreened"))
```


## Overall trend visuals
Two simple but important visuals are plotting one day's worth of data, and the overall trend.
```{r}
source('basic_plots.R')
one_day_plot(no2)
yearly_comparison("World")
```




## Changes over time
We test the significance of the decrease in NO2 from all pairs of consecutive years between 2015 and 2020. 
```{r}
source('change_over_time.R')
t.test.main()
```

# Lockdown correlation
We also assessed the correlation between % change in no2 from 2020 to the mean of 2015-2019 to governmental lockdown data.
```{r}
source('correlation_no2_lockdown.R')
corr.table <- corr.main()
round(corr.table, 2)
```

